### 2020-11-24 README.Rmd
Started the_data_files.Rmd vignette

This is a basic example which illustrates the generation of an initial equilibrium. It uses built in data-sets but usually you would generate zoneC (constants) and zoneD (the dynamic components) from the conditioning data:

>>>>

This is an example which illustrates the generation of an initial equilibrium, which then goes on to apply an early version of the Tasmania MCDA using only 100 replicates (that bit takes about 15 seconds on my computer, hence 2.5 minutes for 1000). It uses built in data-sets but usually you would read in a control file, which would contain the name of the biological datafile describing each population.
